---
title: "**Analyse exploratoire multidimensionnelle des données**"
subtitle: "Application sous Python avec scientisttools 0.1.4"
author: "Duvérier DJIFACK ZEBAZE"
geometry: "left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm, twoside=true"
documentclass: report
fontsize: 11pt
line-height: 1.5
urlcolor: blue
linkcolor: blue
link-citations : yes
nocite:
- '@hurlin2019machine'
- "@provenzano2020machine"
- "@tasche2009estimating"
- "@engelmann2003testing"
- "@hand1997construction"
- "@van2019calibration"
- "@brunel2019fermi"
- "@wright1999numerical"
- "@gill2019practical"
- "@bonnans2006numerical"
- "@bonnans1999numerical"
- "@gill1972quasi"
- "@battiti1992first"
- "@bottou2010large"
- "@bottou2012stochastic"
- "@kingma2014adam"
- "@anderson2007credit"
- "@james2013introduction"
- "@kassambara2018machine"
- "@dumitrescu2021machine"
- "@shofiyah2018split"
- "@dastile2020statistical"
- "@li2019issues"
- "@friedman2009elements"
output: 
  pdf_document:
    highlight: kate
    number_sections : yes
    toc_depth : 0
    df_print: kable
    latex_engine: xelatex
mainfont: Bookman Old Style
papersize: a4
#bibliography: references.bib
biblio-style: apalike
header-includes:
- \usepackage{pbox}
- \usepackage{caption}
- \usepackage{natbib}
- \usepackage[utf8]{inputenc}
- \usepackage[french]{babel}
- \usepackage{amsmath, amsfonts, amssymb}
- \usepackage{amsfonts}
- \usepackage{minitoc}
- \mtcsetdepth{minitoc}{1}
- \mtcsettitle{minitoc}{Sommaire}
- \usepackage{diagbox}
- \usepackage{lettrine}
- \usepackage[labelfont=bf]{caption}
- \captionsetup{font=scriptsize}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{minitoc}
- \usepackage[Bjornstrup]{fncychap}
- \usepackage[dvipsnames]{xcolor}
- \usepackage{fourier-orns}
- \usepackage{fancyhdr}
- \usepackage{geometry}
- \geometry{a4paper,total={160mm,240mm},left=25mm,right=25mm,top=25mm,bottom=25mm}
- \usepackage{amsthm,thmtools,xcolor}
- \usepackage{tcolorbox}
---


\newtheorem{exemple}{Exemple}[chapter]
\newtheorem{proposition}{Proposition}[chapter]
\newtheorem{propriete}{Propriété}[chapter]
\newtheorem{definition}{Définition}[chapter]
\newtheorem{remarque}{Remarque}[chapter]
\newtheorem{exercice}{Exercice}[chapter]
\newtheorem{solution}{Solution}[section]
\newtheorem{quiz}{Quiz}[section]



\mtcsetdepth{minitoc}{1} 
\mtcsettitle{minitoc}{Sommaire}
\newcommand{\Chapter}[1]{\chapter{#1}\minitoc}
\setlength{\parindent}{0em}
\setlength{\parskip}{1.15ex}

\newpage
\dominitoc
\renewcommand{\thepage}{\roman{page}}
\setcounter{page}{1}
\pagenumbering{roman}

\setcounter{tocdepth}{1}
\tableofcontents


\newpage
\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE]{\nouppercase{\thepage\hfill\leftmark}}
\fancyhead[RO]{\nouppercase{\rightmark\hfill\thepage}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0pt}

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
library(reticulate)
library(knitr)
library(kableExtra)
knitr::opts_chunk$set(echo = TRUE,message=FALSE, warning=FALSE,fig.pos = "h",
                      out.extra = "",fig.align = "center", collapse =  FALSE, 
                      highlight = TRUE,out.width = "100%")
```


```{python, echo = FALSE}
import warnings
import matplotlib.pyplot as plt
import warnings
warnings.simplefilter(action='ignore', category=FutureWarning)
warnings.filterwarnings("ignore")
plt.style.use('ggplot')
```


```{r child = "chapter1.Rmd"}

```


```{r child = "chapter2.Rmd"}

```

```{r child = "chapter3.Rmd"}

```

```{r child = "chapter4.Rmd"}

```

```{r child = "chapter5.Rmd"}

```

```{r child = "chapter6.Rmd"}

```






